### 2020-01-30 initial/notes.tex
overplot vertical lines for slowest spin such that CS2 is still stable to tides

Let's return to the simple EOM considered in the constant $\eta$ tides case,
where
\begin{align}
    \pd{\phi}{t} &= -\mu + \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
        \cos \phi} ,\\
    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s*{\epsilon \p*{1 - \mu^2}},
\end{align}
We want to determine where tides destroys CS2. We saw before that tides tends to
shift CS2/CS4 towards each other. In fact, we can immediately see where they
will collide: in the $\dot{\mu}$ equation, no $\phi$ is stationary if
\begin{equation}
    \epsilon > \frac{\eta \sin I}{1 - \mu^2}.
\end{equation}
We can substitute in $\mu_2, \mu_4 \sim \eta \cos I$ to obtain
\begin{equation}
    \epsilon_{c} \approx \frac{\eta \sin I}{1 - \eta^2\cos^2 I}.
\end{equation}

>>>>

Let's return to the simple EOM considered in the constant $\eta$ tides case,
where
\begin{align}
    \pd{\phi}{t} &= -\mu + \eta\p*{\cos I + \sin I \frac{\mu}{\sqrt{1 - \mu^2}}
        \cos \phi} ,\\
    \pd{\mu}{t} &= -\eta \sin I \sin \phi + \s*{\epsilon \p*{1 - \mu^2}},
\end{align}
We want to determine where tides destroys CS2. We saw before that tides tends to
shift CS2/CS4 towards each other. In fact, we can immediately see where they
will collide: in the $\dot{\mu}$ equation, no $\phi$ is stationary if
\begin{equation}
    \epsilon > \frac{\eta \sin I}{1 - \mu^2}.
\end{equation}
Note that we can invert this to find, for a given $\epsilon$, the smallest value
of $\eta$ for which CS2 is still stable, which must satisfy $\eta \sin I =
\epsilon\p*{1 - \eta^2\cos^2 I}$, or
\begin{equation}
    \eta_{\min} \equiv \frac{\sin I + \sqrt{\sin^2I
        + 4\epsilon^2 \cos^2 I}}{2\epsilon \cos^2 I}.
\end{equation}

We can substitute in $\mu_2, \mu_4 \sim \eta \cos I$ to obtain
\begin{equation}
    \epsilon_{c} \approx \frac{\eta \sin I}{1 - \eta^2\cos^2 I}.
\end{equation}
